Output Summary

### 2023-07-15 03-post-process/ms-content/ms-content.Rmd
Add ms-content figure: comparison of survival rates

---
output: 
  pdf_document:
    keep_tex: true
params:
  scenario:
    label: "Scenario"
    value: "base_vlong"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  beta_fig:
    value: TRUE
  relationship_fig:
    value: TRUE
  no_fall_fig:
    value: TRUE
header-includes:
  - \usepackage{sansmathfonts}
  - \usepackage{helvet}
  - \renewcommand{\rmdefault}{\sfdefault}
  - \usepackage{float}
  - \usepackage[labelfont={bf,sc},labelsep=period]{caption}
  - \captionsetup{width=\textwidth}
editor_options: 
  chunk_output_type: console
---

@@

no_fall_caption = "
  Ratios between the across-year mean (dark grey) and coefficient of variation (light grey) abundance of natural-origin smolt reaching Lower Granite Dam with (denominator) and without (numerator) the fall migrant life history strategy.
  The 'without' scenario was calculated by assuming all parr recruits experienced freshwater survival rates of spring migrants.
  Mean ratios <1 and CV ratios >1 indicate LGR smolt abundance would be lower and more variable, respectively, in the absence of the fall migrant strategy.
  Values presented are posterior means and 95% credible regions.
"
```

@@

>>>>

---
output: 
  pdf_document:
    keep_tex: true
params:
  scenario:
    label: "Scenario"
    value: "base_vlong"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  beta_fig:
    value: TRUE
  relationship_fig:
    value: TRUE
  no_fall_fig:
    value: TRUE
  surv_compare_fig:
    value: TRUE
header-includes:
  - \usepackage{sansmathfonts}
  - \usepackage{helvet}
  - \renewcommand{\rmdefault}{\sfdefault}
  - \usepackage{float}
  - \usepackage[labelfont={bf,sc},labelsep=period]{caption}
  - \captionsetup{width=\textwidth}
editor_options: 
  chunk_output_type: console
---

@@

no_fall_caption = "
  Ratios between the across-year mean (dark grey) and coefficient of variation (light grey) abundance of natural-origin smolt reaching Lower Granite Dam with (denominator) and without (numerator) the fall migrant life history strategy.
  The 'without' scenario was calculated by assuming all parr recruits experienced freshwater survival rates of spring migrants.
  Mean ratios <1 and CV ratios >1 indicate LGR smolt abundance would be lower and more variable, respectively, in the absence of the fall migrant strategy.
  Values presented are posterior means and 95% credible regions.
"

surv_compare_caption = "
  Survival probability parameters estimated by the state-space model, separated by stage transition and other demographic features (migratory type, origin, population) where applicable.
  Small points show posterior means of year-specific realized values (jitter for visual effect only) and large points show the average across years.
  Information about mortality due to sources/stages not displayed here was either assumed known without error (e.g., prespawn mortality) or expressed as strong prior information with no inter-annual variability (i.e., mortality experienced in ocean-1 $\\to$ ocean-2 and ocean-2 $\\to$ ocean-3).
"
```

@@

```{r compare-fn, eval = params$surv_compare_fig | params$apportion_compare_fig}
pch = c(21, 23)

cex_main = 2.5
cex_sub = 1.1

solid_col = "grey40"
tranp_col = alpha(solid_col, 0.25)

f_horiz = function(ests1, ests2, lim, label) {
  # prepare the first group of estimates
  ests1 = ests1[-1,]; x1 = colMeans(ests1)

  # figure out the correct axis labels
  if (ncol(ests1) == 4) tick_labels = pops else tick_labels = c("NOR", "HOR")
  jitter = runif(nrow(ests1), -0.25, 0.25)

  if (is.null(ests2)) {
    # empty barplot with correct dimensions
    mp = barplot(x1, col = "white", border = "white", xlim = lim, ylim = c(ncol(ests1) + 0.5, 0.05), horiz = TRUE)

    # figure out location of jittered points
    mp_all = t(sapply(1:nrow(ests1), function(i) mp))
    mp_all = apply(mp_all, 2, function(x) x + jitter)

    # draw year-specific estimates
    points(ests1, mp_all, col = solid_col, bg = tranp_col, pch = pch[1], cex = cex_sub)

    # draw year averages
    points(x1, mp, pch = pch[1], col = "white", bg = "black", cex = cex_main, lwd = 1.5)

    # draw axis
    omgp = par("mgp"); nmgp = omgp; nmgp[2] = 0.15
    par(mgp = nmgp)
    usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
    segments(usr[1], usr[3], usr[1], usr[4], xpd = TRUE, col = par("col.axis"))
    axis(side = 2, at = mp, labels = tick_labels, las = 1)
    par(mgp = omgp)

  } else {
    # prepare the second group of estimates if supplied
    ests2 = ests2[-1,]; x2 = colMeans(ests2)

    # empty barplot with correct dimensions
    mp = barplot(rbind(x1, x2), beside = TRUE, space = c(0.25,1), col = "white", border = "white", xlim = lim, ylim = c(ncol(ests1) * 3 + 1, 0.15), horiz = TRUE)
    mp1 = mp[1,]; mp2 = mp[2,]

    # figure out location of jittered points
    mp1_all = t(sapply(1:nrow(ests1), function(i) mp1))
    mp1_all = apply(mp1_all, 2, function(x) x + jitter)
    mp2_all = t(sapply(1:nrow(ests2), function(i) mp2))
    mp2_all = apply(mp2_all, 2, function(x) x + jitter)

    # draw year-specific estimates
    points(ests1, mp1_all, col = solid_col, bg = tranp_col, pch = pch[1], cex = cex_sub)
    points(ests2, mp2_all, col = solid_col, bg = tranp_col, pch = pch[2], cex = cex_sub)

    # draw year averages
    points(x1, mp1, pch = pch[1], cex = cex_main, bg = "black", col = "white", lwd = 1.5)
    points(x2, mp2, pch = pch[2], cex = cex_main, bg = "black", col = "white", lwd = 1.5)

    # draw axis
    omgp = par("mgp"); nmgp = omgp; nmgp[2] = 0.15
    par(mgp = nmgp)
    usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
    segments(usr[1], usr[3], usr[1], usr[4], xpd = TRUE, col = par("col.axis"))
    axis(side = 2, at = (mp1 + mp2)/2, labels = tick_labels, las = 1)
    par(mpg = omgp)
  }

  # draw panel label
  panel_label(label, y_inp = ifelse(ncol(ests1) == 4, 0.05, 0.1), cex = 1.2)
}

legend_f = function(title, grp1, grp2, loc = "topright") {
  legend(loc, title = title, legend = c(grp1, grp2), pch = pch, pt.cex = 1.3, cex = 0.9, bty = "n",
         text.col = par("col.axis"), col = "black", pt.bg = "black")
}
```

```{r surv-compare-fig, fig.width = 3.4, fig.height = 8, fig.cap = msdown::prep_caption(surv_compare_caption), time_it = TRUE, eval = params$surv_compare_fig}

# extract the posterior means to plot
phi_E_Pb = array_format(post_summ(post, sub_index("^phi_E_Pb[year,pop]", year = observable, pop = ".+"))["mean",])
phi_Pa_Mb_fall = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = observable, pop = ".+", LH_type = i_fall))["mean",])[,i_fall,]
phi_Pa_Mb_spring = array_format(post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = observable, pop = ".+", LH_type = i_spring))["mean",])[,i_spring,]
phi_Mb_Ma_nor = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = observable, pop = ".+", LH_type = i_spring, origin = o_nor))["mean",])[,i_spring,o_nor,]
phi_Mb_Ma_hor = array_format(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = observable, pop = ".+", LH_type = i_spring, origin = o_hor))["mean",])[,i_spring,o_hor,]
phi_Ma_O0 = array_format(post_summ(post, sub_index("^phi_Ma_O0[year,origin]", year = observable, origin = ".+"))["mean",])
phi_O0_O1_nor = array_format(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = observable, pop = ".+", origin = o_nor))["mean",])[,o_nor,]
phi_O0_O1_hor = array_format(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = observable, pop = ".+", origin = o_hor))["mean",])[,o_hor,]
phi_Rb_Ra = array_format(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]", year = observable, origin = ".+"))["mean",])

# set MIN to NA for HOR values
phi_Mb_Ma_hor[,j_min] = NA
phi_O0_O1_hor[,j_min] = NA

mypar(mfrow = c(1,1), oma = c(1.5,1,0,1), col.axis = "black")
layout(matrix(1:5, ncol = 1), height = c(1,1,1,0.5,1))
f_horiz(ests1 = phi_E_Pb, ests2 = NULL, lim = c(0, 0.5), label = "(a) Egg \u2192 Parr")

f_horiz(ests1 = phi_Pa_Mb_fall, ests2 = phi_Pa_Mb_spring, lim = c(0,1), label = "(b) Parr \u2192 Smolt")
legend_f("Mig. Type", "Fall", "Spring")

f_horiz(ests1 = phi_Mb_Ma_nor, ests2 = phi_Mb_Ma_hor, lim = c(0,1), label = "(c) Smolt \u2192 LGR")
legend_f("Origin", "NOR", "HOR")

f_horiz(ests1 = phi_Ma_O0, ests2 = phi_Rb_Ra, lim = c(0,1), label = "(d) Mainstem")
legend_f("Direction", "LGR \u2192 BON", "BON \u2192 LGR", "bottomleft")

f_horiz(ests1 = phi_O0_O1_nor, ests2 = phi_O0_O1_hor, lim = c(0,0.4), label = "(e) Ocean-0 \u2192 Ocean-1")
legend_f("Origin", "NOR", "HOR", "bottomright")
axis_labels("Survival Probability")
```
